Proving linearizability using forward simulations\thanks{An extended version of this paper including the missing proofs can be found at \cite{extended}.}

### 2017-05-05 draftCAV/queue.tex
Deterministic rules.

\begin{minipage}[t]{7.5cm}
\vspace{-3mm}
\begin{lstlisting}
rule inv(enq,x,k):
  $\mathsf{present}$(k) := true
  $\mathsf{pending}$(k) := true
  $\mathsf{arg}$(k) := x
  forall k1 with $\mathsf{present}$(k1)$\land \neg \mathsf{pending}$(k1):
    $\mathsf{before}$(k1,k) := true

rule lin(deq,y,k):
  choose a $\in$ $\mathbb{B}$
  if $($a$\vee\forall k'. \mathsf{present}(k')$=false$) \land \forall k'. \mathsf{present}(k')\Rightarrow \mathsf{pending}(k')$:
    y := EMPTY
  else:
    choose k1 $\in$ $\<Ops>$ with $\mathsf{present}$(k1)$\land\neg \exists k'. \mathsf{present}(k')\land \mathsf{before}(k',$k1$)$
    $\mathsf{present}$(k1) := false
    y := $\mathsf{arg}$(k1)

\end{lstlisting}
\end{minipage}
\begin{minipage}[t]{5cm}
\vspace{-3mm}
\begin{lstlisting}
rule ret(enq,k):
  $\mathsf{pending}$(k) := false

rule inv(deq,k):
  skip

rule ret(deq,y,k):
  return y

>>>>

\begin{minipage}[t]{7.5cm}
\vspace{-3mm}
\begin{lstlisting}
rule inv(enq,v):
  let k = new $\mathbb{O}$
  $\mathsf{present}$(k) := true
  $\mathsf{pending}$(k) := true
  $\mathsf{arg}$(k) := v
  forall k' with $\mathsf{present}$(k')$\land \neg \mathsf{pending}$(k'):
    $\mathsf{before}$(k',k) := true

rule lin(enq,v):
  pass

rule ret(enq,v):
  let k with $\mathsf{arg}$(k) = v
  $\mathsf{pending}$(k) := false

\end{lstlisting}
\end{minipage}
\begin{minipage}[t]{5cm}
\vspace{-3mm}
\begin{lstlisting}
rule inv(deq,v):
  pass

rule lin(deq,v):
  if v = EMPTY:
    forall k with $\mathsf{present}$(k):
      assert $\mathsf{pending}$(k)
  else:
    assert $\mathsf{present}$(k)
    let k with $\mathsf{arg}$(k) = v
    forall k' with $\mathsf{present}$(k'):
      assert $\lnot\mathsf{before}$(k', k)
    $\mathsf{present}$(k) := false

rule ret(deq,v):
  pass
